InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

db_beh2<- db_beh
db328$filename<- as.character(db328$filename)
db328$ssid<- as.character(db328$ssid)

@@

unique(db_beh2$ssid)
# create one column for arousl and RT

@@

colnames(db_beh2)
db_beh2$triggeracq<- db_beh2$trigger
unique(db_beh2$ssid)

@@

colnames(db_beh3)
colnames(db_beh3_301_309)
db_beh3$trigger<-NULL
db_beh3_301_309$triggeracq<- NULL

db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"
db_beh3$condition[db_beh3$condition == "Example Stimuli"]<- "Practice"

db_beh3$triggeracq<- NULL

@@

db_beh3$ssid<- as.numeric(db_beh3$ssid)
# rm(tmp.df4_sum_full_t)

tmp.df4_sum_full<- left_join(tmp.df4_sum, db_beh_all, by = c('ssid', 'tNo'))

>>>>

db_beh2<- db_beh

# problem
db328$filename<- as.character(db328$filename)
db328$ssid<- as.character(db328$ssid)

@@

unique(db_beh2$ssid)

# create one column for arousl and RT

@@

colnames(db_beh2)

db_beh2$triggeracq<- db_beh2$trigger
unique(db_beh2$ssid)

@@

colnames(db_beh3)

colnames(db_beh3_301_309)

db_beh3$trigger<-NULL
db_beh3_301_309$triggeracq<- NULL

db_beh3_301_309$condition[db_beh3_301_309$condition == "Example Stimuli"]<- "Practice"

db_beh3$condition[db_beh3$condition == "Example Stimuli"]<- "Practice"

# db_beh3$triggeracq<- NULL

@@

db_beh3$ssid <- as.numeric(db_beh3$ssid)
# rm(tmp.df4_sum_full_t)

tmp.df4_sum_full<- left_join(tmp.df4_sum, db_beh_all, by = c('ssid', 'tNo'))
tmp.df4_sum_full$ssid<- as.numeric(tmp.df4_sum_full$ssid)

tmp.df4_sum_full<- left_join(tmp.df4_sum_full, db_beh3, by = c('ssid', 'tNo'))
